\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-11 manuscript.tex
first commit

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth]{RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
    {\includegraphics[width=.85\linewidth]{BoxWhisker.drawio.png}}
\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
    \label{fig: Box-beard plot}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig9.eps}%
        \label{fig: weight NAC-L2}}
    \vfill
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig10.eps}%
        \label{fig: weight NAC-eMod}}
    \vfill
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig8.eps}%
        \label{fig: weight NAC-CO}}
    \vfill
    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: weight}
\end{figure}

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig6.eps}%
        \label{fig: error NAC-L2}}
    \vfill
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig7.eps}%
        \label{fig: error NAC-eMod}}
    \vfill
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig5.eps}%
        \label{fig: error NAC-CO}}
    \vfill
    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: error}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig12.eps}%
    \label{fig: weight per layer NAC-CO}}
    \vfill
    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig11.eps}%
    \label{fig: multipliers NAC-CO}}
    \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
    \label{fig: weight and multiplier}
\end{figure}

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth]{fig/RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
    {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
    \label{fig: Box-beard plot}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
        \label{fig: weight NAC-L2}}
    \vfill
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
        \label{fig: weight NAC-eMod}}
    \vfill
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
        \label{fig: weight NAC-CO}}
    \vfill
    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: weight}
\end{figure}

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
        \label{fig: error NAC-L2}}
    \vfill
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
        \label{fig: error NAC-eMod}}
    \vfill
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
        \label{fig: error NAC-CO}}
    \vfill
    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: error}
\end{figure}

@@

\begin{figure}[!t]      
    \centering
    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
    \label{fig: weight per layer NAC-CO}}
    \vfill
    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
    \label{fig: multipliers NAC-CO}}
    \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
    \label{fig: weight and multiplier}
\end{figure}
